---
title: "Tutorial: Basic Classfication"
output: html_notebook
date: 06-10-2019
---

https://dahtah.github.io/imager/imager.html

## Normalize path
```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
knitr::opts_knit$set(root.dir=normalizePath('../../')) 
#library(tidyverse)
```

## Installation
```{r}
install.packages("imager")
library(imager)
```

## Preprocess the data

### Coordinates:
CImg uses standard image coordinates: the origin is at the top left corner, with the x axis pointing right and the y axis pointing down. imager uses the same coordinate system, except the origin is now (1,1) and not (0,0) (the reason being that R indices start at 1 and not at 0). The number of pixels along the x axis is called the width, along the y axis it’s height, along the z axis it’s depth and finally the number of colour channels is called “spectrum”.

```{r}
file <- list.files("data/Havelock_West", pattern="JPG", full.names = TRUE)
im <- load.image(file[1])
dim(im) #5472 3648    1    3 => x,y,z (depth or time), c (color)

plot(im)
```

### subsetting the image
```{r}
imsub(im, x > 1 & x <100, y>1 & y<100) %>% plot

imsub(im, x > 1000 & x <1100, y>1 & y<100) %>% plot
```

```{r}
an <- read.csv("data/Havelock_West/export-2019-06-11T02_47_41.367Z.csv")

corn <- gsub("\"|grass.*", "", an$Label) 

```

```{r}
R(im) %>% plot(main="Red channel along 10th row",type="l")
RGBtoHSL(im) %>% plot
```





