---
title: "Tutorial: Basic Classfication"
output: html_notebook
date: 06-10-2019
---

https://dahtah.github.io/imager/imager.html

## Normalize path
```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
knitr::opts_knit$set(root.dir=normalizePath('../../')) 
#library(tidyverse)
```

## Installation
```{r}
install.packages("imager")
library(imager)
```

## Preprocess the data

### Coordinates:
CImg uses standard image coordinates: the origin is at the top left corner, with the x axis pointing right and the y axis pointing down. imager uses the same coordinate system, except the origin is now (1,1) and not (0,0) (the reason being that R indices start at 1 and not at 0). The number of pixels along the x axis is called the width, along the y axis it’s height, along the z axis it’s depth and finally the number of colour channels is called “spectrum”.

```{r}
file <- list.files("data/Havelock_West", pattern="JPG", full.names = TRUE)
im <- load.image(file[1])
dim(im) #5472 3648    1    3 => x,y,z (depth or time), c (color)

plot(im)
```

### subsetting the image
```{r}
imsub(im, x > 1 & x <100, y>1 & y<100) %>% plot

imsub(im, x > 1000 & x <1100, y>1 & y<100) %>% plot
```

```{r}
an <- read.csv("data/Havelock_West/export-2019-06-11T02_47_41.367Z.csv")

corn <- gsub("\"|grass.*", "", an$Label) 
s1 <- unlist(strsplit(corn, split="geometry:"))[-1]
s2 <- unlist(strsplit(s1, split="\\},\\{"))
s3 <- gsub("\\[|\\]|\\{|\\}|\\,", "", s2)

df <- as.data.frame(matrix(s3, ncol=4, byrow=TRUE))
df$x1 <- as.numeric(gsub("y:.*|x:", "", df$V1))
df$x2 <- as.numeric(gsub("y:.*|x:", "", df$V3))
df$y1 <- as.numeric(gsub(".*y:", "", df$V1))
df$y2 <- as.numeric(gsub(".*y:", "", df$V2))
df <- df[order(df$x1, df$y1),]
```



```{r}
i =2
imsub(im, x > df$x1[i] & x < df$x2[i], y>df$y1[i] & y< df$y2[i]) %>% plot

```


```{r}
par(mfcol=c(4,5))
par(mar=c(0, 0, 1.5, 0), xaxs='i', yaxs='i')
for (i in 1:20) { 
  img <- imsub(im, x > df$x1[i] & x < df$x2[i], y>df$y1[i] & y< df$y2[i])
  img <- t(apply(img, 2, rev)) 
  image(1:28, 1:28, img, col = gray((0:255)/255), xaxt = 'n', yaxt = 'n')
}
```



### Setup the ML layers (cat or dog page 124)

```{r}
rm(list=ls())
library(keras)

model <- keras_model_sequential() %>%
    layer_conv_2d(filters =32, kernel_size=c(3,3), activation="relu",
                  input_shape = c(10, 10, 3)) %>% #height, width, and RGB
    layer_max_pooling_2d(pool_size=c(2,2)) %>%
    layer_conv_2d(filters =64, kernel_size=c(3,3), activation="relu") %>%
    layer_max_pooling_2d(pool_size=c(2,2)) %>%
    layer_flatten() %>%
    layer_dense(units = 512, activation = 'relu') %>%
    layer_dense(units = 2, activation = 'softmax')

summary(model)
```


### Compile the Model

```{r}
model %>% compile(
  optimizer = 'adam', 
  loss = 'sparse_categorical_crossentropy',
  metrics = c('accuracy')
)
```

### Train the model

```{r}
model %>% fit(train_images, train_labels, epochs = 5)
```

### Evaluate accuracy

```{r}
score <- model %>% evaluate(test_images, test_labels)

cat('Test loss:', score$loss, "\n")
cat('Test accuracy:', score$acc, "\n")
```















