---
title: "Havelock Data preprocessing"
output: html_notebook
date: 06-12-2019
---

https://dahtah.github.io/imager/imager.html

## Normalize path
```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
knitr::opts_knit$set(root.dir=normalizePath('../../')) 
#library(tidyverse)
```


# Using the test data

corn, grass and soil


```{r}
an <- read.csv("data/Havelock_West/export-2019-06-11T02_47_41.367Z.csv")




corn <- gsub("\"|grass.*", "", an$Label) 
s1 <- unlist(strsplit(corn, split="geometry:"))[-1]
s2 <- unlist(strsplit(s1, split="\\},\\{"))
s3 <- gsub("\\[|\\]|\\{|\\}|\\,", "", s2)

df1 <- as.data.frame(matrix(s3, ncol=4, byrow=TRUE))
df1$x1 <- as.numeric(gsub("y:.*|x:", "", df1$V1))
df1$x2 <- as.numeric(gsub("y:.*|x:", "", df1$V3))
df1$y1 <- as.numeric(gsub(".*y:", "", df1$V1))
df1$y2 <- as.numeric(gsub(".*y:", "", df1$V2))
df1 <- df1[order(df1$x1, df1$y1),]


grass <- gsub("\"|soil.*", "", an$Label) 
grass <- gsub(".*grass", "grass", grass)
s1 <- unlist(strsplit(grass, split="geometry:"))[-1]
s2 <- unlist(strsplit(s1, split="\\},\\{"))
s3 <- gsub("\\[|\\]|\\{|\\}|\\,", "", s2)

df2 <- as.data.frame(matrix(s3, ncol=4, byrow=TRUE))
df2$x1 <- as.numeric(gsub("y:.*|x:", "", df2$V1))
df2$x2 <- as.numeric(gsub("y:.*|x:", "", df2$V3))
df2$y1 <- as.numeric(gsub(".*y:", "", df2$V1))
df2$y2 <- as.numeric(gsub(".*y:", "", df2$V2))
df2 <- df2[order(df2$x1, df2$y1),]

soil <- gsub("\"", "", an$Label) 
soil <- gsub(".*soil", "soil", soil)
s1 <- unlist(strsplit(soil, split="geometry:"))[-1]
s2 <- unlist(strsplit(s1, split="\\},\\{"))
s3 <- gsub("\\[|\\]|\\{|\\}|\\,", "", s2)

df3 <- as.data.frame(matrix(s3, ncol=4, byrow=TRUE))
df3$x1 <- as.numeric(gsub("y:.*|x:", "", df3$V1))
df3$x2 <- as.numeric(gsub("y:.*|x:", "", df3$V3))
df3$y1 <- as.numeric(gsub(".*y:", "", df3$V1))
df3$y2 <- as.numeric(gsub(".*y:", "", df3$V2))
df3 <- df3[order(df3$x1, df3$y1),]


```



## chop data into 10x10 small images

```{r}
file <- list.files("data/Havelock_West", pattern="JPG", full.names = TRUE)
im <- load.image(file[1])
dim(im) #5472 3648    1    3 => x,y,z (depth or time), c (color)

#plot(im)
```



```{r}
library(imager)
chopimg <- function(df=df1, path="data/test/corn/", im){
    
    ### change to nearest 10 values
    df$x10 <- ceiling((df$x1-1)/10)*10+1
    df$x20 <- floor((df$x2)/10)*10
    df$y10 <- ceiling((df$y1-1)/10)*10+1
    df$y20 <- floor((df$y2)/10)*10
    
    stat1 <- nrow(df) ## input annotations
    df <- subset(df, x20 > x10 & y20 > y10)
    stat2 <- nrow(df) ## useful annotations
    message(sprintf("###>>> useful/input [%s / %s] annotations ...", stat1, stat2))
    
    df$pics <- -9
    for(i in 1:nrow(df)){
        
        xs <- seq(from=df$x10[i], to=df$x20[i], by=10)
        ys <- seq(from=df$y10[i], to=df$y20[i], by=10)
        
        gs <- data.frame(x=rep(xs, each=length(ys)), y=rep(ys, times=length(xs)))
        
        for(j in 1:nrow(gs)){
            outfile=paste0(path,"/test_x", gs$x[j], "_y", gs$y[j], ".png")
            #imsub(im, x > 1 & x <10, y>1 & y<10) %>% plot
            save.image(imsub(im, x > gs$x[j] & x < (gs$x[j]+10), y > gs$y[j] & y < (gs$y[j]+10)), file=outfile)
        }
        df$pics[i] <- nrow(gs)
    }
    return(df)
}

t1 <- chopimg(df=df1, path="data/test/corn/", im)
t2 <- chopimg(df=df2, path="data/test/grass/", im)
```



















```{r}
base_dir <- "~/Downloads/cats_and_dogs_small"
dir.create(base_dir)
train_dir <- file.path(base_dir, "train")
dir.create(train_dir)
validation_dir <- file.path(base_dir, "validation")
dir.create(validation_dir)
test_dir <- file.path(base_dir, "test")
dir.create(test_dir)
train_cats_dir <- file.path(train_dir, "cats")
dir.create(train_cats_dir)
train_dogs_dir <- file.path(train_dir, "dogs")
dir.create(train_dogs_dir)
validation_cats_dir <- file.path(validation_dir, "cats")
dir.create(validation_cats_dir)
validation_dogs_dir <- file.path(validation_dir, "dogs")
dir.create(validation_dogs_dir)
test_cats_dir <- file.path(test_dir, "cats")
dir.create(test_cats_dir)
test_dogs_dir <- file.path(test_dir, "dogs")
dir.create(test_dogs_dir)
fnames <- paste0("cat.", 1:1000, ".jpg")
file.copy(file.path(original_dataset_dir, fnames), 
          file.path(train_cats_dir)) 
fnames <- paste0("cat.", 1001:1500, ".jpg")
file.copy(file.path(original_dataset_dir, fnames), 
          file.path(validation_cats_dir))
fnames <- paste0("cat.", 1501:2000, ".jpg")
file.copy(file.path(original_dataset_dir, fnames),
          file.path(test_cats_dir))
fnames <- paste0("dog.", 1:1000, ".jpg")
file.copy(file.path(original_dataset_dir, fnames),
          file.path(train_dogs_dir))
fnames <- paste0("dog.", 1001:1500, ".jpg")
file.copy(file.path(original_dataset_dir, fnames),
          file.path(validation_dogs_dir)) 
fnames <- paste0("dog.", 1501:2000, ".jpg")
file.copy(file.path(original_dataset_dir, fnames),
          file.path(test_dogs_dir))
```




- Read the pic files
- Decode the JPEG content to RBG grids of pixels
- Convert these into floating point tensors
- Rescale to 0-1








## Installation
```{r}
install.packages("imager")
library(imager)
```

## Preprocess the data

### Coordinates:
CImg uses standard image coordinates: the origin is at the top left corner, with the x axis pointing right and the y axis pointing down. imager uses the same coordinate system, except the origin is now (1,1) and not (0,0) (the reason being that R indices start at 1 and not at 0). The number of pixels along the x axis is called the width, along the y axis it’s height, along the z axis it’s depth and finally the number of colour channels is called “spectrum”.

```{r}
file <- list.files("data/Havelock_West", pattern="JPG", full.names = TRUE)
im <- load.image(file[1])
dim(im) #5472 3648    1    3 => x,y,z (depth or time), c (color)

plot(im)
```

### subsetting the image
```{r}
imsub(im, x > 1 & x <10, y>1 & y<10) %>% plot

imsub(im, x > 1000 & x <1100, y>1 & y<100) %>% plot
```

```{r}
an <- read.csv("data/Havelock_West/export-2019-06-11T02_47_41.367Z.csv")

corn <- gsub("\"|grass.*", "", an$Label) 
s1 <- unlist(strsplit(corn, split="geometry:"))[-1]
s2 <- unlist(strsplit(s1, split="\\},\\{"))
s3 <- gsub("\\[|\\]|\\{|\\}|\\,", "", s2)

df <- as.data.frame(matrix(s3, ncol=4, byrow=TRUE))
df$x1 <- as.numeric(gsub("y:.*|x:", "", df$V1))
df$x2 <- as.numeric(gsub("y:.*|x:", "", df$V3))
df$y1 <- as.numeric(gsub(".*y:", "", df$V1))
df$y2 <- as.numeric(gsub(".*y:", "", df$V2))
df <- df[order(df$x1, df$y1),]
```



```{r}
i =2
imsub(im, x > df$x1[i] & x < df$x2[i], y>df$y1[i] & y< df$y2[i]) %>% plot

```


```{r}
par(mfcol=c(4,5))
par(mar=c(0, 0, 1.5, 0), xaxs='i', yaxs='i')
for (i in 1:20) { 
  img <- imsub(im, x > df$x1[i] & x < df$x2[i], y>df$y1[i] & y< df$y2[i])
  img <- t(apply(img, 2, rev)) 
  image(1:28, 1:28, img, col = gray((0:255)/255), xaxt = 'n', yaxt = 'n')
}
```



### Setup the ML layers (cat or dog page 124)

```{r}
rm(list=ls())
library(keras)

model <- keras_model_sequential() %>%
    layer_conv_2d(filters =32, kernel_size=c(3,3), activation="relu",
                  input_shape = c(10, 10, 3)) %>% #height, width, and RGB
    layer_max_pooling_2d(pool_size=c(2,2)) %>%
    layer_conv_2d(filters =64, kernel_size=c(3,3), activation="relu") %>%
    layer_max_pooling_2d(pool_size=c(2,2)) %>%
    layer_flatten() %>%
    layer_dense(units = 512, activation = 'relu') %>%
    layer_dense(units = 2, activation = 'softmax')

summary(model)
```


### Compile the Model

```{r}
model %>% compile(
  optimizer = 'adam', 
  loss = 'sparse_categorical_crossentropy',
  metrics = c('accuracy')
)
```

### Train the model

```{r}
model %>% fit(train_images, train_labels, epochs = 5)
```

### Evaluate accuracy

```{r}
score <- model %>% evaluate(test_images, test_labels)

cat('Test loss:', score$loss, "\n")
cat('Test accuracy:', score$acc, "\n")
```















